\subsection{Ampersand for government organization}\label{subsection:ampersand-for-government-organization}
The sub-question "\acrlong{RQ4}" focuses on the use of Ampersand within the \acrshort{cibg} organization.
The information systems that are not based on legislation and regulations and which aim to monitor data quality are often the registers.
\acrshort{cibg} builds, manages and monitors this data through registration systems.

\input{docs/AF-SE/23_discussion/234_rq4/234_rq4_1_s}

\input{docs/AF-SE/23_discussion/234_rq4/234_rq4_2_w}

\input{docs/AF-SE/23_discussion/234_rq4/234_rq4_3_o}

\input{docs/AF-SE/23_discussion/234_rq4/234_rq4_4_t}

\input{docs/AF-SE/23_discussion/234_swot}

The design of register systems has no specific points for attention.
Part of the research question was about designing for register systems.
Other than the source specific link, the \acrshort{big}, no particulars were found for registry systems.
The translation of this law into an information system results in a register.
The requirements of the register are laid down by law.
This concerned, among other things, the identifying data of a registration and in Article 3, paragraph 1~\footnote{\url{https://wetten.overheid.nl/jci1.3:c:BWBR0006251&hoofdstuk=II&paragraaf=1&article=3&z=2022-04-01&g=2022-04-01}} it says it is about multiple registers.
This also explains why there are few observations about registration systems.
The register system therefore does not stand alone, but is a consequence of the fact that the source is a law.