\def\rq{RQ4}
\input{docs/AF-SE/22_results/counterdef}
\acrlong{\rq}
\paragraph{Ampersand}
\begin{enumerate}
    \item rq4-1 Ampersand cannot calculate.
    But since \A{Ampersand} is static, process data can be monitored in other ways.
    \newline\textbf{obs}: Ampersand cannot calculate.

    \item rq4-7 What happens if \A{Ampersand} is implemented and there are changes in the structure (normal for software)
    \newline\textbf{obs}: When a new model is created within Ampersand, the data structure is reloaded.
    There are no provisions for preserving the data that has already been entered.

    \item rq4-8:22-11: The team behind \A{Ampersand} is very dedicated.
    \newline\textbf{obs}: Calls are resolved quickly.
    Example was the error message on wrong multiplicity.
    (notification \url{https://github.com/AmpersandTarski/RAP/issues/128})
    Reloading a new version is not easy.

\end{enumerate}

\paragraph{Api}
\begin{enumerate}
    \item rq4-2 The \A{api} link works fine, but entire messages return.
    These should actually get codes.
    \newline\textbf{obs}: An api returned a text.
    Calling applications usually don't handle that very well.
    It is usual to return a code and sometimes with text.
    Think of http response codes.

    \item rq4-5 Postman used for \A{api} link with Ampersand.
    \newline\textbf{obs}: As a test it is possible to use Postman for the link.
    So it is not necessary to build an application for this.

\end{enumerate}

\paragraph{Architecture}
\begin{enumerate}
    \item rq4-3 Embedding in \A{architecture}
     %\newline rq4-6 ui model;
     Law core with shared concepts and process part.
     The core of law is specific law.
     Shared concepts are also part of the law but also occur elsewhere.
     This is part of embedding in architecture.
     \newline\textbf{obs}: Embedding into the existing architecture is important for usability, in the form of acceptance.

\end{enumerate}

\paragraph{Interface}
\begin{enumerate}
    \item rq4-4 The \A{interface} produces many messages and these remain.
    \newline\textbf{obs}: Prototype screens fill up with messages when they are not resolved.

\end{enumerate}

\input{docs/AF-SE/22_results/tabledef}
\newpage
